Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/conclusion.tex
Add conclusion
Shrink conclusions

Cyber-physical systems must be tolerant to cyber-attacks in the same way they are tolerant to faults. The DARPA CASE program is creating an MBSE environment for designers to integrate cyber-vulnerability analysis and mitigation through the design process to harden systems early in the design process. BriefCASE is the result of that program, and it provides cyber-analysis tools that add cyber requirements to the AGREE specification for the design and architectural transforms with AGREE specifications to satisfy the cyber requirements. BriefCASE is fully integrated into the OSATE AADL modeling environment for ease of use by system engineers.

The filter architectural transformation in BriefCASE prevents malformed data from being propagated downstream to other components while the monitor transformation enforces temporal properties to detect when untrusted components behave maliciously. The components are specified by corresponding auto-generated AGREE contracts that only require the system designer to state the policies to enforce.These can be adapted from the cyber requirements in the system design. The specifications are automatically synthesized to CakeML that can then be compiled to a wide array of backend targets. The synthesis to CakeML is done in a way that preserves the meaning of the specifications.

The BriefCASE tool suite demonstrated in action on a full-scale case study with the UxAS open source UAV AI planning system. The complex system requires several architectural transformations to meet cyber-requirements, and the entire system is synthesized and deployed on the seL4 platform running on ODRIOD using the synthesis tool described here and the BriefCASE HAMR tool to generate the communication fabric. The size and scale of the case study gives some evidence that BriefCASE, with its transformations, scales to the complexity demands often seen in real-world design.

Ongoing work is using BriefCASE on the Collin' Common Avionics Architecture System (CAAS) in the context of a CH47 rotor wing platform. The filter and monitor transformations are being employed to protect against \emph{Automatic Dependent Surveillance-Broadcast} (ADS-B) spoofing by malicious actors in the airspace. That work is expanding synthesis with uninterpreted functions to support non-linear and transcendental functions. Other ongoing work is mechanizing the synthesis proof in HOL4 and lifting the proof results given for finite streams to infinite streams.

>>>>

The DARPA CASE program is creating an MBSE environment for designers to integrate cyber-vulnerability analysis and mitigation. The resulting BriefCASE tool suite in OSATE includes analyses to add cyber requirements to systems and architectural transformations on systems to satisfy cyber requirements. The filter transformation prevents malformed data from being propagated downstream while the monitor transformation checks temporal properties to detect malicious behavior. The components are specified by corresponding auto-generated AGREE contracts that only require policy annotations taken from the cyber requirements. The specifications are automatically synthesized to CakeML and that synthesis preserves the meaning of the specifications.

The BriefCASE analyses and transformations are applied to a full-scale case study on the Air Force Research Laboratory's OpenUxAS services requiring several filters and monitors to meet cyber-requirements. A video shows the synthesized system running on the ODROID platform with seL4. The size and scale of the study suggests BriefCASE meets the complexity demands of real-world design.

Ongoing work is applying BriefCASE in the Collin' Common Avionics Architecture System (CAAS), \cite{caas}, to protect against \emph{Automatic Dependent Surveillance-Broadcast} spoofing. That work adds support for uninterpreted functions. Other ongoing work is mechanizing the synthesis proof in HOL4 and lifting the proof results to infinite streams.
